---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ln.knn.regression

<!-- badges: start -->
# codecov badge for code coverage
[![codecov](https://codecov.io/gh/DSCI-310/dsci-310-group-09-pkg/branch/main/graph/badge.svg?token=gOMgyT71QL)](https://codecov.io/gh/DSCI-310/dsci-310-group-09-pkg)
<!-- badges: end -->

The goal of ln.knn.regression is to assist in creating a regression analysis project. It includes functions that help to explore and summarize the data. It also includes functions that directly build linear and k-nn models. Additionally, it contains functions that can test the model's error and accuracy. 

## Installation

You can install the development version of ln.knn.regression from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-09-pkg")
```

## Example

This is a basic example which shows you how to use the functions for EDA:

```{r example1}
library(ln.knn.regression)

summarize_column(mtcars, mtcars$mpg)

hist_plot(mtcars, mpg, "MPG", "Count", "Histogram for MPG of Cars", 10)

```

Here is an example of how to build a linear regression model:

```{r, include = FALSE, echo = FALSE}
set.seed(100)
mtcars_split <- rsample::initial_split(mtcars)
mtcars_training <- rsample::training(mtcars_split)
mtcars_testing <- rsample::testing(mtcars_split)
```

```{r example2}
mtcars_model <- linearmodel(recipes::recipe(mpg ~ hp, mtcars_training), mtcars_training)
mtcars_model
```

Now we can create a scatter plot that shows the best fit line from the model:

```{r example3}
scatter_plot(mtcars_training, 
             hp, 
             mpg, 
             "Horse Power (HP)", 
             "Miles Per Gallon (mpg)",
             "Best Fit Line for MPG vs HP", 
             15,
             "lm") 
```

Finally, we can test the model's error by finding the RMSPE value:

```{r example4}
mtcars_rmspe <- model_rmspe(mtcars_model, mtcars_testing, "mpg")
mtcars_rmspe
```
This tells us that the model has a prediction error of around `r format(round(mtcars_rmspe,2))` miles per gallon when tested on data it has not seen before.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.


Another useful function in this package is `scatter_plot()`. It takes in the variables `var1`,`var2`, the labels of the x-axis `xlab` and for the y-axis `ylab`, a title of the scatter plot `title`, and `text_size` to specify the size of text of the labels and title. 


The useful function allows you to generate a simple scatter plot with the essential parameters to aid the visualization of your analysis. It makes sure that each parameter is the right type whether it is a data frame, numeric value, or string and produces an error if one does not have the right type of input.
