---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ln.knn.regression

<!-- badges: start -->
[![codecov](https://codecov.io/gh/DSCI-310/dsci-310-group-09-pkg/branch/main/graph/badge.svg?token=gOMgyT71QL)](https://codecov.io/gh/DSCI-310/dsci-310-group-09-pkg)
<!-- badges: end -->

The goal of `ln.knn.regression` is to assist in creating a regression analysis project from start to finish. It includes functions that help to explore, summarize and visualize the data. It also includes functions that directly build and visualize linear and k-nn models. Additionally, it contains functions that can test the model's error and accuracy. 

## Installation

You can install the development version of ln.knn.regression from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-09-pkg")
```

## Functions

* `bar_graph()`
* `hist_plot()`
* `knn_model()`
* `linearmodel()`
* `model_rmspe()`
* `scatter_plot()
* `summarize_column()`

## Example

This is a basic example which shows you how to explore the data and build a linear regression model.

### 1. EDA

```{r EDA}
library(ln.knn.regression)

summarize_column(mtcars, mtcars$mpg)

hist_plot(mtcars, mpg, "MPG", "Count", "Histogram for MPG of Cars", 10)

```

### 2. Model Building

```{r, include = FALSE, echo = FALSE}
set.seed(100)
mtcars_split <- rsample::initial_split(mtcars)
mtcars_training <- rsample::training(mtcars_split)
mtcars_testing <- rsample::testing(mtcars_split)
```

```{r model}
mtcars_model <- linearmodel(recipes::recipe(mpg ~ hp, mtcars_training), mtcars_training)
mtcars_model
```

### 3. Visualizations 

```{r visualization}
scatter_plot(mtcars_training, 
             hp, 
             mpg, 
             "Horse Power (HP)", 
             "Miles Per Gallon (mpg)",
             "Best Fit Line for MPG vs HP", 
             15,
             "lm") 
```

### 4. Finding model's accuracy 

```{r rmspe}
mtcars_rmspe <- model_rmspe(mtcars_model, mtcars_testing, "mpg")
mtcars_rmspe
```
This tells us that the model has a prediction error of around `r format(round(mtcars_rmspe,2))` miles per gallon when tested on data it has not seen before.

## Contributing

We appreciate contributions to the `ln.knn.regression` package. Please refer to our [Contributing document](https://github.com/DSCI-310/dsci-310-group-09-pkg/blob/main/CONTRIBUTING.md) and [Code of Conduct](https://github.com/DSCI-310/dsci-310-group-09-pkg/blob/main/CODE_OF_CONDUCT.md) for more information.

## License

The software provided in this project is offered under the [MIT open source license](https://opensource.org/license/mit/). Refer to the [license file](https://github.com/DSCI-310/dsci-310-group-09-pkg/blob/main/LICENSE.md) for more information.
